miniKanren with fair search strategies

### 2019-05-02 Paper/paper.tex
correct source of reverso
improve figure names

\begin{figure}
	\lstinputlisting{Figures/balanced-disj.rkt}
	\caption{\texttt{balanced-disj}}
	\label{balanced-disj}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/fDFS.rkt}
	\caption{How fDFS differs from iDFS}
	\label{fDFS}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/BFS-opt.rkt}	
	\caption{interface functions in optimized BFS (pure)}
	\label{BFS-opt}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
	\caption{interface functions in optimized BFS (impure)}
	\label{BFS-opt-cont}
\end{figure}

@@

In this section, we compare the pure subset of our optimized BFS with the BFS 
found in \citep{seres1999algebra}. We focus on the pure subset because 
Silvija's system is pure.

@@

;;TODO check if reverso and appendo are absolutely the same as the ones in TRS2.

\begin{table}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline 
		benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  
		\\
		\hline
		very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
		& 300000 & 2160 & 2836 &    - & 6137 &    - \\
		\hline 
		appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
		& 300 & 617 & 634 & 593 & 631 & 622 \\ 
		\hline 
		reverseo & 10 &   5 &   3 &   3 &     38 &     85 \\ 
		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
		& 30 & 446 & 442 & 485 & 123288 & 132159 \\ 
		\hline
		quine-1 & 1 &  71 &  44 & 69 & - & - \\ 
		& 2 & 127 & 142 & 95 & - & - \\ 
		& 3 & 114 & 114 & 93 & - & - \\ 
		\hline
		quine-2 & 1 & 147 & 112 &  56 & - & - \\ 
		& 2 & 161 & 123 & 101 & - & - \\ 
		& 3 & 289 & 189 & 104 & - & - \\ 
		\hline 
		'(I love you)-1 &  99 & 56 & 15 & 22 &  74 & 165 \\ 
		& 198 & 53 & 72 & 55 &  47 &  74 \\
		& 297 & 72 & 90 & 44 & 181 & 365 \\ 
		\hline
		'(I love you)-2 &  99 & 242 &  61 & 16 &  66 &  99 \\ 
		& 198 & 445 & 110 & 60 &  42 &  64 \\
		& 297 & 476 & 146 & 49 & 186 & 322 \\ 
		\hline 
	\end{tabular}
	\caption{The results of a quantitative evaluation: running times of 
	benchmarks 
		in milliseconds}
	\label{compare-efficiency}
\end{table}

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
memory. The first three benchmarks are taken from 
\citep{friedman_reasoned_2018}. Next two benchmarks about quine are modified 
from a similar test case in \citep{byrd2017unified}. The modifications are made 
to circumvent the need for symbolic constraints (e.g. $\neq$, 
\texttt{absento}). Our version generates de 
Bruijnized expressions and prevent closures getting into list. The two 
benchmarks differ in the \conde clause order of their relation interpreters. 
The last two 
benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
sibling benchmarks differ in the \conde clause order of their relation 
interpreters. The first one 
has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
end, while the other has them at the beginning. We conjecture that iDFS would 
perform badly in the second case because elimination rules complicate the 
problem when running backward. The evaluation supports our conjecture.

>>>>

\begin{figure}
	\lstinputlisting{Figures/balanced-disj.rkt}
	\caption{biDFS implementation}
	\label{balanced-disj}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/fDFS.rkt}
	\caption{fDFS implementation}
	\label{fDFS}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/BFS-opt.rkt}	
	\caption{new and changed functions in optimized BFS that implements pure 
	features}
	\label{BFS-opt}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/BFS-opt-cont.rkt}	
	\caption{new and changed functions in optimized BFS that implements impure 
		features}
	\label{BFS-opt-cont}
\end{figure}

@@

In this section, we compare the pure subset of our optimized BFS with the BFS 
found in \citep{seres1999algebra}. We focus on the pure subset because 
Silvija's system is pure. Her system represents search spaces with streams of 
lists of states, where each list is a bag.

@@

\begin{table}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline 
		benchmark & size & iDFS & biDFS & fDFS & optimized BFS & Silvija's BFS  
		\\
		\hline
		very-recursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
		& 300000 & 2160 & 2836 &    - & 6137 &    - \\
		\hline 
		appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
		& 300 & 617 & 634 & 593 & 631 & 622 \\ 
		\hline 
		reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
		& 30 & 446 & 442 & 485 & 123288 & 132159 \\ 
		\hline
		quine-1 & 1 &  71 &  44 & 69 & - & - \\ 
		& 2 & 127 & 142 & 95 & - & - \\ 
		& 3 & 114 & 114 & 93 & - & - \\ 
		\hline
		quine-2 & 1 & 147 & 112 &  56 & - & - \\ 
		& 2 & 161 & 123 & 101 & - & - \\ 
		& 3 & 289 & 189 & 104 & - & - \\ 
		\hline 
		'(I love you)-1 &  99 & 56 & 15 & 22 &  74 & 165 \\ 
		& 198 & 53 & 72 & 55 &  47 &  74 \\
		& 297 & 72 & 90 & 44 & 181 & 365 \\ 
		\hline
		'(I love you)-2 &  99 & 242 &  61 & 16 &  66 &  99 \\ 
		& 198 & 445 & 110 & 60 &  42 &  64 \\
		& 297 & 476 & 146 & 49 & 186 & 322 \\ 
		\hline 
	\end{tabular}
	\caption{The results of a quantitative evaluation: running times of 
	benchmarks 
		in milliseconds}
	\label{compare-efficiency}
\end{table}

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means running out of 
memory. The first two benchmarks are taken from 
\citep{friedman_reasoned_2018}. \texttt{reverso} is from 
\citep{rozplokhas2018improving}. Next two benchmarks 
about quine are modified from a similar test case in \citep{byrd2017unified}. 
The modifications are made 
to circumvent the need for symbolic constraints (e.g. $\neq$, 
\texttt{absento}). Our version generates de 
Bruijnized expressions and prevent closures getting into list. The two 
benchmarks differ in the \conde clause order of their relation interpreters. 
The last two 
benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
you)}. This benchmark is also inspired by \citep{byrd2017unified}. Again, the 
sibling benchmarks differ in the \conde clause order of their relation 
interpreters. The first one 
has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
end, while the other has them at the beginning. We conjecture that iDFS would 
perform badly in the second case because elimination rules complicate the 
problem when running backward. The evaluation supports our conjecture.
